---
title: "Compare"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{compare}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load the package

```{r setup}
library(flowtracker)
```

# Example

with the flowtracker package you can compare dataframes and test if ... 

first create two datasets with a slight difference:
```{r}
data_before <- mtcars
data_after <- mtcars |> dplyr::filter(cyl != 6)
```

By default, the compare_dfs function expects the data to be equal on all properties.
If a property is different, the evalution will tell you
```{r}
compare_dfs(data_before, data_after)
```

Let's create a different 'after' dataset, with less columns.
```{r}
data_after2 <- dplyr::select(mtcars, -hp)
```

And compare them with the right expectation, namely 'less' columns.
```{r}
compare_dfs(data_before,
            data_after2,
            expect_n_cols = "less",
            expect_colnames = "not_equal")
```
